The Need to Develop a Holistic Infectious Disease Surveillance System

### 2024-09-27 manuscript/manuscript.qmd
Include Julia scripts in manuscript file for plots

  The performance of an outbreak detection system is highly sensitive to the structure and the level of background noise.
  Under the assumption that the noise is relatively static over time (as influenza-like illness was early in the COVID-19 pandemic), RDTs can perform as well as ELISA in a surveillance system.
  However, when the noise is non-stationary, imperfect tests cannot overcome their accuracy limitations through higher testing rates. 
toc: false
tbl-cap-location: bottom
format:
  generic-manuscript-typst:
    keep-typ: true
---

@@

![A schematic of the outbreak definition and alert detection system. A) Noise time series. B) Measles incidence time series. C) Observed time series resulting from testing noise & measles cases that visit the healthcare facility. The orange bands/vertical lines represent regions of the measles time series that meet the outbreak definition criteria. The green bands/vertical lines represent regions of the observed (measles - noise) time series that breach the alert threshold (the horizontal dashed line), and constitute an alert.](./schematic-simulation_with-shade.png){#fig-outbreak-schematic}

@@

>>>>

  The performance of an outbreak detection system is highly sensitive to the structure and the level of background noise.
  Under the assumption that the noise is relatively static over time (as influenza-like illness was early in the COVID-19 pandemic), RDTs can perform as well as ELISA in a surveillance system.
  However, when the noise is non-stationary, imperfect tests cannot overcome their accuracy limitations through higher testing rates. 
toc: false
tbl-cap-location: bottom
format:
  generic-manuscript-typst:
    keep-typ: true
jupyter: julia-1.10
---

@@

```{julia}
#| fig-cap: "A schematic of the outbreak definition and alert detection system. A) Noise time series. B) Measles incidence time series. C) Observed time series resulting from testing noise & measles cases that visit the healthcare facility. The orange bands/vertical lines represent regions of the measles time series that meet the outbreak definition criteria. The green bands/vertical lines represent regions of the observed (measles - noise) time series that breach the alert threshold (the horizontal dashed line), and constitute an alert."
#| label: fig-outbreak-schematic
include("schematic-plot.jl")
```

@@

```{julia}
#| fig-cap: "The accuracy of outbreak detection systems under different testing rates and noise structures. The shaded bands illustrate the 80% central interval, and the solid/dashed lines represent the mean estimate."
#| label: fig-accuracy
include("line-plot.jl")
```
